\begin{thebibliography}{99}
\addcontentsline{toc}{chapter}{Bibliografia}

\bibitem{bloch} F. Bloch, \textit{Über die Quantenmechanik der Elektronen in Kristallgittern}, Z. Phys. (1928), vol. 52: 555–600
\bibitem{mott} H. Jones, N. F. Mott,  H. W. B. Skinner, \textit{A Theory of the Form of the X-Ray Emission Bands of Metals}, Phys. Rev. 45, 379 (1934)
\bibitem{slatter} J. C. Slater, G. F. Koster, \textit{Simplified LCAO Method for the Periodic Potential Problem}, Phys. Rev. 94, 1498 (1954)
\bibitem{kittel} C. Kittel, \textit{Introduction to Solid State Physics, 7th ed.}, Wiley, (1996) 
\bibitem{soc} R. J. Elliott, \textit{Theory of the effect of spin-orbit coupling on magnetic reso-
nance in some semiconductors}, Phys. Rev. 96(2):266–279 (1954).
\bibitem{geim} Andre K. Geim, \textit{Nobel Lecture: Random walk to graphene}, Rev. Mod. Phys. 83, 851 (2011)
\bibitem{brodie} B.C. Brodie, \textit{On the Atomic Weight of Graphite},  Philosophical Transactions of the Royal Society of London 149: 249–259 (1859)
\bibitem{debije} P. Debije, P. Scherrer. \textit{Interferenz an regellos orientierten Teilchen im Röntgenlicht I}, Physikalische Zeitschrift (in German) 17: 277 (1916)
\bibitem{bernal} J. D. Bernal, \textit{The Structure of Graphite}, Proc. R. Soc. Lond. A106 (740): 749–773 (1924)
\bibitem{haenni} V. Kohlschütter, P. Haenni, \textit{Zur Kenntnis des Graphitischen Kohlenstoffs und der Graphitsäure}, Zeitschrift für anorganische und allgemeine Chemie (in German) 105 (1): 121–144  (1919)
\bibitem{wallace} P. R. Wallace, \textit{The Band Structure of Graphite}, Physical Review 71: 622–634 (1947)
\bibitem{divincenzo} D. P. DiVincenzo, E. J. Mele, \textit{Self-Consistent Effective Mass Theory for Intralayer Screening in Graphite Intercalation Compounds}, Physical Review B 295 (4): 1685–1694 (1984)
\bibitem{epitaxial} C. Oshima, A. Nagashima, \textit{Ultra-thin epitaxial films of graphite and hexagonal boron nitride on solid surfaces}, J. Phys.: Condens. Matter 9: 1–20. (1997)
\bibitem{geim-science} K. S. Novoselov, A. K. Geim, S. V. Morozov, D. Jiang; Y. Zhang, S. V. Dubonos, I. V. Grigorieva, A. A. Firsov, \textit{Electric Field Effect in Atomically Thin Carbon Films}, Science 306 (5696): 666–669 (2004)
\bibitem{graphene_review} A. H. Castro Neto et al., \textit{The electronic properties of graphene}, Rev. Mod. Phys., Vol. 81, No. 1, January–March (2009)
\bibitem{boukhvalov} D. W. Boukhvalov, M. I. Katsnelson, A. I. Lichtenstein, \textit{Hydrogen on graphene: Electronic structure, total energy, structural distortions and magnetism
from first-principles calculations}, Phys. Rev. B 77, 035427 (2008)
\bibitem{basics} B. Gharekhanlou, S. Khorasani, \textit{An overview of tight-binding method for two-dimensional carbon structures}, Graphene: synthesis and applications (2011)
\bibitem{slonczewski} J. C. Slonczewski, P. R. Weiss, \textit{Band Structure of Graphite}, Phys. Rev. 109, 272 (1958)
\bibitem{graphene_soc_parameters} T. B. Boykin, M. Luisier, G. Klimeck, X. Jiang, N. Kharche, Y. Zhou, S. K. Nayak, \textit{Accurate six-band nearest-neighbor tight-binding model for the $\pi$-bands of bulk graphene and graphene nanoribbons}, J. Appl. Phys. 109, 104304 (2011)
\bibitem{brei} L. Brey, H. A. Fertig, \textit{Electronic states of graphene nanoribbons studied with the Dirac equation}, Phys. Rev. B 73, 235411 – Published 15 June (2006)
\bibitem{areshkin} D. A. Areshkin, D. Gunlycke, C. T. White, \textit{Ballistic transport in graphene nanostrips in the presence of disorder: importance of edge effects}, Nano Lett. 7, 204 (2007)
\bibitem{barone} V. Barone, O. Hod, G. E. Scuseria, \textit{Electronic structure and stability of semiconducting graphene nanoribbons}, Nano Lett. 6, 2748 (2006)
\end{thebibliography}
